%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,11pt,oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\graphicspath{{images/}}
\usepackage[left=0.6in, right=1in, bottom=0.8in, top=1in]{geometry}
\usepackage{enumitem}
\setlist[itemize]{align=parleft,left=0pt..0.5em,label={-},nosep}

\pagenumbering{gobble}

\hyphenation{MaskRCNN}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%% NAME OF APPLICANT %%%%%%%%%%%%%%%%%%%

\noindent  \LARGE{\textbf{Miroslav Šimko, PhD}}  \\
\vspace{-2ex}
\normalsize

%%%%%%%%%%%%%%%%% CONTACT INFORMATION %%%%%%%%%%%%%%%%%

\begin{center}
\begin{tabular}{l l}
 Computer Vision / Python / C++ Developer & \hspace{1in} \href{mailto:ms@iolabs.ch}{ms@iolabs.ch} \\
  Currently based in Kyoto, Japan & \hspace{1in} Phone: +81 70-9020-3002 \\
  \end{tabular}
  \end{center}

  \vspace{1em}

%%%%%%%%%%%%%%%%% MAIN BODY %%%%%%%%%%%%%%%%%%%%%%%%%%%

  \noindent \begin{tabular}{@{} l l}
  \hline \\
    \begin{tabular}[t]{l} \Large{Professional} \\ \Large{Summary} \end{tabular}
    &
    \begin{minipage}[t]{14.5cm}
    Results-driven Data Analyst and Machine Learning Expert with a proven track
    record of leveraging Python and PyTorch to extract insights from complex datasets.
    Proficient in the application of machine learning algorithms to solve real-world problems,
    with a focus on 3D computer vision and natural language processing. Experienced
    in developing and deploying language model-based solutions, including Large Language
    Models (LLMs), to enhance document understanding and classification tasks. Skilled
    in data visualization, statistical analysis, and model evaluation techniques.
    \end{minipage} \\
    \\
    \hline \\
 \Large{Education}   
     & \textbf{2013--2021, Ph.D.}, Experimental Nuclear and Particle Physics \\
     & {Czech Technical University in Prague (CTU)} \\
     & {Faculty of Nuclear Sciences and Physical Engineering (FNSPE)} \\
     & \textbf{Thesis focus:} Study of Heavy Flavor at the STAR Experiment \\[.3cm]
%      & \\
     & \textbf{2011--2013, M.Sc.}, Experimental Nuclear and Particle Physics (CTU -- FNSPE)\\
     & \textbf{Thesis:} Design and Optimization of the Optical Readout System \\
     & for Electromagnetic Calorimeter FOCAL for the ALICE Experiment \\[.3cm]
%      & \\
     & \textbf{2008--2011, B.Sc.}, Experimental Nuclear and Particle Physics (CTU -- FNSPE)\\
     & \textbf{Thesis:} Detector Control System for the ALICE Experiment \\
     \\
   
  \Large{Experience} & \textbf{2021--present: ioLabs AG, Zurich, Switzerland}\\
    & \textbf{Computer Vision Developer (mostly remotely)}\\
    & \begin{minipage}[t]{14.5cm}
      \begin{itemize}
	\item Developed and trained 3D computer vision models for civil engineering projects.
	\item Led a project on sorting and understanding technical documents using LLM, embedding, and computer vision.
	\item Utilized advanced pruning and quantization techniques, deployed models as APIs
	  on Flask and FastAPI.
	\item Proficient in Python, PyTorch framework, and state-of-the-art models such as 
	  MaskRCNN for 2D and MeshCNN for 3D computer vision.
	\item Developed plugins for Archicad and Vectorworx in C++.
     \end{itemize}
  \vspace{1.7ex}
  \textbf{2019--2020: ioLabs AG, Zurich, Switzerland}\\
  \textbf{Geometry Engine Developer}
      \begin{itemize}
	\item Engineered collision detection algorithms systems using Python and C++.
      \end{itemize}
  \vspace{1.7ex}
  \textbf{2013--2021: Brookhaven National Laboratory (BNL), USA}\\
  \textbf{Experimental Physicist}
      \begin{itemize}
	\item Analyzed data for heavy-flavor particle reconstruction at the STAR experiment.
	\item Utilized "big-data" techniques on computing clusters, employing C++ and Root.
	\item Applied machine learning with the TMVA package (Boosted-Decision Trees).
	\item Managed maintenance and upgrades for the STAR ZDC detector.
      \end{itemize}
  \vspace{1.7ex}
  \textbf{2011--2013: CERN, Switzerland: Detector Control System Expert}
      \begin{itemize}
	\item Managed maintenance and upgrades for Silicon-Drift Detectors at the ALICE experiment.
	\item Developed upgrades in PVSS and contributed to the Prague prototype for the FoCal detector. 
      \end{itemize}
    \end{minipage}\\
  \end{tabular}

  \newpage

%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%%%%%%%%%

  \noindent  \begin{tabular}{@{} l l}
    \begin{tabular}[t]{l}\Large{Languages and Skills} \end{tabular}   
      & 
    \begin{minipage}[t]{10cm}
    Czech/Slovak (native), English (fluent), Japanese (intermediate), French (beginner)  \\[.2cm]
    Python, C++, PyTorch, AWS, Docker, Jenkins, Git, Statistical analysis\\[.2cm]
    Driver's License B
    \end{minipage}\\[.4cm]
    \begin{tabular}[t]{l}\Large{Interests}\end{tabular}    & Physics, Automation, Photography, Sports, Reading \\
  & \\[.1cm]
    \begin{tabular}[t]{l}\Large{Publications and Conferences}\end{tabular}
      & 
    \begin{minipage}[t]{10cm}
      Published article in Physical Review Letters, author on more than 95 collaboration papers.\\
      Presented at 9 international conferences with 3 proceedings papers.
    \end{minipage} \\
  & \\[.5cm]
  \end{tabular}

\noindent \begin{tabular}{@{} l l l}
  \Large{References} & & \\[.3cm]
  & \small Martin Loučka (current employer) & \small Zhangbu Xu (Work on STAR ZDC) \\
  & \small ioLabs AG & \small BNL, USA  \\
  & \small CEO & \small STAR Spokesperson \\
  &  \footnotesize{\href{mailto:ml@iolabs.ch}{ml@iolabs.ch}} &  \footnotesize{\href{mailto:xzb@bnl.gov}{xzb@bnl.gov}} \\[.2cm]
  & \small Jaroslav Bielčík (Former supervisor)& \small  Xin Dong (Supervisor at LBNL) \\
  & \small FNSPE -- CTU & \small LBNL, USA \\
  & \small Head of the Experimental Particle Physics Department & \small  Senior researcher \\
  &  \footnotesize{\href{mailto:jaroslav.bielcik@fjfi.cvut.cz}{jaroslav.bielcik@fjfi.cvut.cz}} &  \footnotesize{\href{mailto:xdong@lbl.gov}{xdong@lbl.gov}} \\[.2cm]
  & \small Jana Bielčíková (Former employer) & \small Vojtěch Petráček (Former supervisor)   \\
  & \small Nuclear Physics Institute, Czech Academy of Sciences & \small CTU \\
  & \small Director of the Nuclear Spectroscopy Department & \small University director  \\
  &  \footnotesize{\href{mailto:jana.bielcikova@ujf.cas.cz}{jana.bielcikova@ujf.cas.cz}}  &  \footnotesize{\href{mailto:vojtech.petracek@fjfi.cvut.cz}{vojtech.petracek@fjfi.cvut.cz}}  \\[.4cm]
\hline \\
  & \textbf{Github page:} & \\
  & \small \url{https://github.com/mirsimko} & \\[.3cm]
  & \textbf{ioLabs AG} & \\
  & \small \url{https://iolabs.ch} & \\
\end{tabular}

\end{document}
